---
title: "Test R Code on Github"
author: Neil J. Gunther
output: 
  github_document:
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r, fig.width=5, fig.height=5, echo=FALSE}
plot(pressure)
```

This plot was resized by using `fig.width=5`, and `fig.height=5` in the `knitr` R chunk. Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


## Including Math

RStudio `knitr` claims to be able to render certain simple inline equations, e.g., $E=mc^2$, as well as display equations like

$$
e^{i \pi} + 1 = 0
$$
and

$$
R = \frac{N}{X} - Z
$$
using LaTex markup notation. However, they do not seem to render correctly either in the local HTML browser or on GitHub.


